### 2015-07-30 Irregular-occ/Irregular-occ.tex
.

We utilize the offsets obtained by \cite{GomesJunior2015} to identify a pattern in the error of the ephemeris. This pattern could be used to extrapolate an offset to the satellite by the time of the occultation predicted. Plots of the offsets over time and true anomaly (see Fig. \ref{Fig:offxtime} and \ref{Fig:offxtanom} for Carme) clearly show that these two parameters are the most important in the differences observed.

>>>>

Making a new model for the orbits of these objects would demand a lot of time and delay the publication of these predictions. Then we utilize the offsets obtained by \cite{GomesJunior2015} to identify a pattern in the error of the ephemeris. This pattern could be used to extrapolate an offset to the satellite ephemeris by the time of the occultation predicted. Plots of the offsets over time and true anomaly (see Fig. \ref{Fig:offxtime} and \ref{Fig:offxtanom} for Carme) clearly show the systematic error in the JPL ephemeris.
